---
title: "Simulations"
output: html_document
date: "2024-01-04"
---

```{r}
library(MASS)
library(lme4)
library(nlme)
library(tidyverse)
library(parallel)
library(doParallel)
library(foreach)
library(gee)
```

```{r}
# Parallel running
if (length(showConnections()) > 0) closeAllConnections()
ncores=detectCores()
cl <- makeCluster(ncores)  
registerDoParallel(cl)
```

```{r}
# Correlation structure
# Exchangeable
exch_cor <- function(n, sigma, rho){
  covmat <- rho * outer(sigma, sigma, `*`)
  diag(covmat) <- sigma^2
  return(covmat)
}

# AR1
ar1_cor <- function(n, sigma, rho){
  rhomat <- rho^abs(outer(1:n, 1:n, `-`))
  covmat <- rhomat*outer(sigma, sigma, `*`)
  diag(covmat) <- sigma^2
  return(covmat)
}

# Correlation term (alpha3)
corr_term = function(numer, denom){
  return(numer/denom)
}

# Convert data to long (full) configuration
# Scale baseline value and center time
convert_long = function(id, time1, y, p){
  datay = data.frame(id, time1, y)
  y1 = rep(datay[datay$time1==0,]$y, each=p)

  ydata_long = datay %>% 
    mutate(y1=y1) %>% 
    mutate(y.1 = scale(y1)[,1]) %>% 
    mutate(timec = time1 - mean(time1))
  return(ydata_long)
}
```

# Write simulation into a whole function

```{r}
# n: sample size
# p: number of observations per subject
# nsim: number of simulations
# alpha: parameter of fixed effects
# D: Covariance matrix of random effect
# R: Covariance matrix of residuals
# convert_long: function that converts data to long (full) configuration

# Function used to obtain k1 through simulations
true_k_est <- function(n,p,nsim, alpha, D, R, convert_long){

id = rep(1:n, each=p)
time1 = rep(0:(p-1),n)

# Fixed effect `alpha` in equation 3.1.
# `t` represents treatment group and `c` represents control group
alpha_t=alpha$alpha_t
alpha_c=alpha$alpha_c

if (is.null(alpha_t) & is.null(alpha_c)){
  stop("Please specify fixed effect.")
} else if (is.null(alpha_t)){
  alpha_t = alpha_c
} else if (is.null(alpha_c)){
  alpha_c = alpha_t
}

# Covariance matrix `D` of random effect `b` in equation 3.1.
# `t` represents treatment group and `c` represents control group
D_t = D$D_t
D_c = D$D_c

if (is.null(D_t) & is.null(D_c)){
  stop("Please specify covariance matrix of random effect.")
} else if (is.null(D_t)){
  D_t = D_c
} else if (is.null(D_c)){
  D_c = D_t
}

# Covariance matrix `R` of residuals `e` in equation 3.1.
# `t` represents treatment group and `c` represents control group
R_t = R$R_t
R_c = R$R_c

if (ncol(R_t) != p | ncol(R_c) != p){
  stop("The dimension of covariance matrix of residuals is not equal to the number of observations per subjects.")
}

if (is.null(R_t) & is.null(R_c)){
  stop("Please specify covariance matrix of residuals.")
} else if (is.null(R_t)){
  R_t = R_c
} else if (is.null(R_c)){
  R_c = R_t
}

# Treatment indicator (1: Treatment, 0: Control)
tx=rep(c(1,0), each=(p*n))
  
beta <- matrix(NA, nsim, 2)

beta <- foreach (i = 1:nsim, .combine=rbind, .packages=c("dplyr","tidyverse", "MASS")) %dopar% {
  Zt = mvrnorm(n, c(0,0), D_t)
  b0it=Zt[,1] # Random intercepts in treatment group 
  b1it=Zt[,2] # Random slopes in treatment group
  
  Zc = mvrnorm(n, c(0,0), D_c)
  b0ic=Zc[,1] # Random intercepts in control group
  b1ic=Zc[,2] # Random slopes in control group
  
  epsilon_t = mvrnorm(n, rep(0,p), R_t) # Residuals in treatment group
  epsilon_c = mvrnorm(n, rep(0,p), R_c) # Residuals in control group
  
  # Create response values for treatment and control group
  yt = (alpha_t[1]+b0it[id]) + (alpha_t[2]+b1it[id])*time1 + c(t(epsilon_t))
  yc = (alpha_c[1]+b0ic[id]) + (alpha_c[2]+b1ic[id])*time1 + c(t(epsilon_c))
  
  # Convert data to long (full) configuration for treatment and control group
  ydata_long = convert_long(id,time1,yt,p)
  ydata_long0 = convert_long(id,time1,yc,p)
  
  # Create Y_1*T variable in equation 2.14 for treatment and control group 
  ydata_long1 = ydata_long %>% mutate(y1_t =y.1*timec)
  cov_mat_trt = cov(ydata_long1)
  ydata_long01 = ydata_long0 %>% mutate(y1_t =y.1*timec)
  cov_mat_cont = cov(ydata_long01)
  
  # Calculate Cov(Y_1*T, Y) for treatment and control group
  y1_t_y_c = cov_mat_cont["y1_t", "y"]
  y1_t_y_t = cov_mat_trt["y1_t", "y"]
  
  # Cov(Y_1*T, Y) for treatment group, Cov(Y_1*T, Y) for control group
  c(y1_t_y_c=y1_t_y_c, y1_t_y_t=y1_t_y_t)
}

mean_obj=colMeans(beta) 
return(mean_obj)
}
```

```{r}
# n: sample size
# p: number of observations per subject
# nsim: number of simulations
# alpha: parameter of fixed effects
# D: Covariance matrix of random effect
# R: Covariance matrix of residuals
# k1: Approximate true k through simulations (by Approach 1)
# k2: k derived directly from model parameters (by Approach 2)
# convert_long: function that converts data to long (full) configuration
# corr_term: function that calculates alpha3

# Function used to compare naive, RCT, and corrected estimates using two approaches
corr_sim <- function(n,p,nsim, alpha, D, R, k1, k2, convert_long, corr_term){

id = rep(1:n, each=p)
time1 = rep(0:(p-1),n)

# Fixed effect `alpha` in equation 3.1.
# `t` represents treatment group and `c` represents control group
alpha_t=alpha$alpha_t
alpha_c=alpha$alpha_c

if (is.null(alpha_t) & is.null(alpha_c)){
  stop("Please specify fixed effect.")
} else if (is.null(alpha_t)){
  alpha_t = alpha_c
} else if (is.null(alpha_c)){
  alpha_c = alpha_t
}

# Covariance matrix `D` of random effect `b` in equation 3.1.
# `t` represents treatment group and `c` represents control group
D_t = D$D_t
D_c = D$D_c

if (is.null(D_t) & is.null(D_c)){
  stop("Please specify covariance matrix of random effect.")
} else if (is.null(D_t)){
  D_t = D_c
} else if (is.null(D_c)){
  D_c = D_t
}

# Covariance matrix `R` of residuals `e` in equation 3.1.
# `t` represents treatment group and `c` represents control group
R_t = R$R_t
R_c = R$R_c

if (ncol(R_t) != p | ncol(R_c) != p){
  stop("The dimension of covariance matrix of residuals is not equal to the number of observations per subjects.")
}

if (is.null(R_t) & is.null(R_c)){
  stop("Please specify covariance matrix of residuals.")
} else if (is.null(R_t)){
  R_t = R_c
} else if (is.null(R_c)){
  R_c = R_t
}

# Treatment indicator (1: Treatment, 0: Control)
tx=rep(c(1,0), each=(p*n))
  
beta <- matrix(NA, nsim, 4)

beta <- foreach (i = 1:nsim, .combine=rbind, .packages=c("dplyr","tidyverse", "MASS", "gee")) %dopar% {
  Zt = mvrnorm(n, c(0,0), D_t)
  b0it=Zt[,1] # Random intercepts in treatment group 
  b1it=Zt[,2] # Random slopes in treatment group
  
  Zc = mvrnorm(n, c(0,0), D_c)
  b0ic=Zc[,1] # Random intercepts in control group
  b1ic=Zc[,2] # Random slopes in control group

  epsilon_t = mvrnorm(n, rep(0,p), R_t) # Residuals in treatment group
  epsilon_c = mvrnorm(n, rep(0,p), R_c) # Residuals in control group
  
  # Create response values for treatment and control group
  yt = (alpha_t[1]+b0it[id]) + (alpha_t[2]+b1it[id])*time1 + c(t(epsilon_t))
  yc = (alpha_c[1]+b0ic[id]) + (alpha_c[2]+b1ic[id])*time1 + c(t(epsilon_c))
  
  # Convert data to long (full) configuration for treatment and control group
  ydata_long = convert_long(id,time1,yt,p)
  ydata_long0 = convert_long(id,time1,yc,p)
  
  # Combine data from treatment and control group
  ytotal = rbind(ydata_long, ydata_long0)
  
  # Add treatment indicator variable 
  ytotal2 = cbind(ytotal,tx)
  
  # Get naive estimate
  mod.naive = gee(y~timec*y.1, data=ydata_long, id=id, corstr = "AR-M", Mv=1)
  beta.naive=coef(mod.naive)[4]
  
  # Get RCT estimate
  mod.rct =  gee(y~timec*y.1*tx, data=ytotal2, id=id, corstr = "AR-M", Mv=1)
  beta.rct = coef(mod.rct)[8]
  
  # Create Y_1*T variable in equation 2.14 for treatment group
  ydata_long1 = ydata_long %>% mutate(y1_t =y.1*timec)
  cov_mat_trt = cov(ydata_long1)
  
  # Calculate correction term (alpha3) using k1
  alpha3_1 = corr_term(numer=k1*cov_mat_trt["y1_t", "y"], denom=cov_mat_trt["y1_t", "y1_t"])
  
  # Get Corrected estimate using Approach 1 (k1)
  beta.cor_1 = beta.naive-alpha3_1
  
  # Calculate correction term (alpha3) using k2
  alpha3_2 = corr_term(numer=k2*cov_mat_trt["y1_t", "y"], denom=cov_mat_trt["y1_t", "y1_t"])
  
  # Get Corrected estimate using Approach 2 (k2)
  beta.cor_2 = beta.naive-alpha3_2
  
  # Naive estimate, RCT estimate, Corrected estimate using Approach 1 and 2
  c(beta.naive, beta.rct, beta.cor_1, beta.cor_2)
}

mean=colMeans(beta) 
st_dev=apply(beta, 2, sd)

result = rbind(mean,st_dev)
return(result)
}
```


# Reference Scenario (Scenario 1)
```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=5000,p=3,nsim=10000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```


```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
# Scenario 1
(-0.655-(-0.658))^2 + 0.252^2 # Approach 1 
(-0.450-(-0.658))^2 + 0.174^2 # Approach 2
```

```{r}
# Line plot of bias of corrected estimator against k varying from 1.50 to 2.50. k1 = 1.97 (red),k2 = 1.67 (blue).

k = c(1.5,1.6,1.67,1.8,1.9,1.97,2.0,2.1,2.2,2.3,2.4,2.5)
bias = c(0.325,0.257,0.208,0.112,0.048,0.003,-0.01,-0.075,-0.163,-0.215,-0.289,-0.318)

plot_bias_dat = data.frame(cbind(k,bias))

plot_bias_dat %>% 
  ggplot(aes(x=k,y=bias))+
    geom_point()+
    geom_line()+
    geom_segment(aes(x = 1.97, xend = 1.97, y = -0.4, yend = 0.003), color = "red",linetype="dashed")+
    geom_segment(aes(x = 1.67, xend = 1.67, y = -0.4, yend = 0.208), color = "blue",linetype="dashed")+
    geom_point(aes(x=1.97, y=0.003), colour="red", cex=2.5)+
    geom_point(aes(x=1.67, y=0.208), colour="blue", cex=2.5)+
    coord_cartesian(ylim = c(-0.33, 0.33))+
    labs(y="Bias")+
    theme_bw()

ggsave('bias_k.png')
```


# Perturbation of Fixed Effects

## Scenario 2: alpha_c = (55,0)
```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,0)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```

```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(-0.646-(-0.658))^2 + 0.261^2 # Approach 1 
(-0.443-(-0.658))^2 + 0.179^2 # Appoach 2
```

## Scenario 3: alpha_c = (55,-2)
```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,-2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```

```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(-0.656-(-0.658))^2 + 0.258^2 # Approach 1 
(-0.452-(-0.658))^2 + 0.177^2 # Approach 2
```

## Scenario 4: alpha_c = (55,4)
```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,4)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```

```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(-0.655-(-0.658))^2 + 0.246^2 # Approach 1 
(-0.450-(-0.658))^2 + 0.169^2 # Approach 2
```


# Perturbation of Random Effects

## Scenario 5: sigma_1 = 3.5 for treatment and sigma_1 = 2 for control group

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 2
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```


```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(0.046-(0.047))^2 + 0.017^2 # Approach 1 
(0.032-(0.047))^2 + 0.012^2 # Approach 2
```

## Scenario 6: sigma_1 = 3.5 for treatment and sigma_1 = 2.5 for control group

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 2.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```

```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(-0.192-(-0.188))^2 + 0.073^2 # Approach 1 
(-0.129-(-0.188))^2 + 0.049^2 # Approach 2
```

## Scenario 7: sigma_1 = 3.5 for treatment and sigma_1 = 4 for control group

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 4
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```


```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(-0.907-(-0.893))^2 + 0.351^2 # Approach 1 
(-0.615-(-0.893))^2 + 0.238^2 # Approach 2
```


## Scenario 8: rho = 0.3 for treatment and rho = 0.6 for control group

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.6
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```


```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(-0.982-(-0.986))^2 + 0.401^2 # Approach 1 
(-0.667-(-0.986))^2 + 0.272^2 # Approach 2
```

## Scenario 9: rho = 0.3 for treatment and rho = 0.3 for control group

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.3
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```

```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
# 0 # Approach 1
# 0 # Approach 2
```


## Scenario 10: rho = 0.3 for treatment and rho = 0.2 for control group

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.2
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```


```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(-0.325-(-0.328))^2 + 0.128^2 # Approach 1 
(-0.222-(-0.328))^2 + 0.088^2 # Approach 2
```


# Perturbation of Residuals

## Scenario 11: sigma_r1=sigma_r2=sigma_r3=2 for treatment, sigma_r1=2, sigma_r2=2.5, sigma_r3=3 for control

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = c(2,2.5,3)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```


```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(-0.678-(-0.674))^2 + 0.267^2 # Approach 1 
(-0.451-(-0.674))^2 + 0.177^2 # Approach 2
```

## Scenario 12: sigma_r1=sigma_r2=sigma_r3=2 for treatment, sigma_r1=2, sigma_r2=1.5, sigma_r3=1 for control

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = c(2,1.5,1)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```


```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(-0.639-(-0.642))^2 + 0.259^2 # Approach 1 
(-0.448-(-0.642))^2 + 0.181^2 # Approach 2
```

## Scenario 13: sigma_r1=sigma_r2=sigma_r3=2 for treatment, sigma_r1=2, sigma_r2=2, sigma_r3=2 for control. rho_r for control = 0.4.

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.4
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```


```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(-0.677-(-0.681))^2 + 0.257^2 # Approach 1 
(-0.446-(-0.681))^2 + 0.169^2 # Approach 2
```


## Scenario 14: sigma_r1=sigma_r2=sigma_r3=2 for treatment, sigma_r1=2, sigma_r2=2, sigma_r3=2 for control. rho_r for control = 0.2.

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.2
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```


```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(-0.642-(-0.641))^2 + 0.246^2 # Approach 1 
(-0.453-(-0.641))^2 + 0.174^2 # Approach 2
```


## Scenario 15: Exchangeable correlation, sigma_r1 = sigma_r2 = sigma_r3 = 2, rho_r = 0.3

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Get k directly from model parameters (k2)
k2 = (corr_c*sigma_time1_c)/(corr_t*sigma_time1_t)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=exch_cor(p,sd_t,rho_t)
R_c=exch_cor(p,sd_c,rho_c)

true_k_est_v = true_k_est(n=1000,p=3,nsim=5000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)

# Estimate true k values through simulations (k1)
k1 = true_k_est_v[1]/true_k_est_v[2]

c(k1,k2)
```


```{r}
# Naive, RCT, Corrected estimates using Approach 1 and 2
corr_sim(n=200,p=3,nsim=1000, alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), k1=k1, k2=k2, convert_long, corr_term)
```

```{r}
# Calculating MSE
(-0.653-(-0.656))^2 + 0.230^2 # Approach 1 
(-0.496-(-0.656))^2 + 0.175^2 # Approach 2
```


