---
title: "Truth"
output: html_document
date: "2024-01-04"
---

```{r}
library(MASS)
library(lme4)
library(nlme)
library(tidyverse)
library(parallel)
library(doParallel)
library(foreach)
library(gee)
```

```{r}
# Parallel running
if (length(showConnections()) > 0) closeAllConnections()
ncores=detectCores()
cl <- makeCluster(ncores)  
registerDoParallel(cl)
```

```{r}
# Correlation structure
# Exchangeable
exch_cor <- function(n, sigma, rho){
  covmat <- rho * outer(sigma, sigma, `*`)
  diag(covmat) <- sigma^2
  return(covmat)
}

# AR1
ar1_cor <- function(n, sigma, rho){
  rhomat <- rho^abs(outer(1:n, 1:n, `-`))
  covmat <- rhomat*outer(sigma, sigma, `*`)
  diag(covmat) <- sigma^2
  return(covmat)
}

# Convert data to long (full) configuration
# Scale baseline value and center time
convert_long = function(id, time1, y, p){
  datay = data.frame(id, time1, y)
  y1 = rep(datay[datay$time1==0,]$y, each=p)

  ydata_long = datay %>% 
    mutate(y1=y1) %>% 
    mutate(y.1 = scale(y1)[,1]) %>% 
    mutate(timec = time1 - mean(time1))
  return(ydata_long)
}
```


```{r}
# n: sample size
# p: number of observations per subject
# nsim: number of simulations
# alpha: parameter of fixed effects
# D: Covariance matrix of random effect
# R: Covariance matrix of residuals
# convert_long: function that converts data to long (full) configuration

# Function used to calculate true estimate through simulations
cal_truth <- function(n,p,nsim, alpha, D, R, convert_long){

id = rep(1:n, each=p)
time1 = rep((0:(p-1)),n)

# Fixed effect `alpha` in equation 3.1.
# `t` represents treatment group and `c` represents control group
alpha_t=alpha$alpha_t
alpha_c=alpha$alpha_c

if (is.null(alpha_t) & is.null(alpha_c)){
  stop("Please specify fixed effect.")
} else if (is.null(alpha_t)){
  alpha_t = alpha_c
} else if (is.null(alpha_c)){
  alpha_c = alpha_t
}

# Covariance matrix `D` of random effect `b` in equation 3.1.
# `t` represents treatment group and `c` represents control group
D_t = D$D_t
D_c = D$D_c

if (is.null(D_t) & is.null(D_c)){
  stop("Please specify covariance matrix of random effect.")
} else if (is.null(D_t)){
  D_t = D_c
} else if (is.null(D_c)){
  D_c = D_t
}

# Covariance matrix `R` of residuals `e` in equation 3.1.
# `t` represents treatment group and `c` represents control group
R_t = R$R_t
R_c = R$R_c

if (ncol(R_t) != p | ncol(R_c) != p){
  stop("The dimension of covariance matrix of residuals is not equal to the number of observations per subjects.")
}

if (is.null(R_t) & is.null(R_c)){
  stop("Please specify covariance matrix of residuals.")
} else if (is.null(R_t)){
  R_t = R_c
} else if (is.null(R_c)){
  R_c = R_t
}

# Treatment indicator (1: Treatment, 0: Control)
tx=rep(c(1,0), each=(p*n))
  
beta <- matrix(NA, nsim, 1)

beta <- foreach (i = 1:nsim, .combine=rbind, .packages=c("dplyr","tidyverse", "MASS", "gee")) %dopar% {
  Zt = mvrnorm(n, c(0,0), D_t)
  b0it=Zt[,1] # Random intercepts in treatment group 
  b1it=Zt[,2] # Random slopes in treatment group
  
  Zc = mvrnorm(n, c(0,0), D_c)
  b0ic=Zc[,1] # Random intercepts in control group
  b1ic=Zc[,2] # Random slopes in control group

  epsilon_t = mvrnorm(n, rep(0,p), R_t) # Residuals in treatment group
  epsilon_c = mvrnorm(n, rep(0,p), R_c) # Residuals in control group
  
  # Create response values for treatment and control group
  yt = (alpha_t[1]+b0it[id]) + (alpha_t[2]+b1it[id])*time1 + c(t(epsilon_t))
  yc = (alpha_c[1]+b0ic[id]) + (alpha_c[2]+b1ic[id])*time1 + c(t(epsilon_c))
  
  # Convert data to long (full) configuration for treatment and control group
  ydata_long = convert_long(id,time1,yt,p)
  ydata_long0 = convert_long(id,time1,yc,p)
  
  # Combine data from treatment and control group
  ytotal = rbind(ydata_long, ydata_long0)
  
  # Add treatment indicator variable
  ytotal2 = cbind(ytotal,tx)
  
  # Get true estimate (truth)
  mod.rct = lm(y~timec*y.1*tx, data=ytotal2)
  beta.truth = coef(mod.rct)[8]
  
  c(beta.truth)
}

mean=colMeans(beta) 
st_dev=apply(beta, 2, sd)

result = rbind(mean,st_dev)
return(result)
}
```

# Reference Scenario (Scenario 1)
```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)
```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


# Perturbation of Fixed Effects

## Scenario 2: alpha_c = (55,0)
```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,0)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)
```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


## Scenario 3: alpha_c = (55,-2)
```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,-2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


## Scenario 4: alpha_c = (55,4)
```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,4)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)


# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


# Perturbation of Random Effects

## Scenario 5: sigma_1 = 3.5 for treatment and sigma_1 = 2 for control group

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 2
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


## Scenario 6: sigma_1 = 3.5 for treatment and sigma_1 = 2.5 for control group

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 2.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


## Scenario 7: sigma_1 = 3.5 for treatment and sigma_1 = 4 for control group

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 4
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


## Scenario 8: rho = 0.3 for treatment and rho = 0.6 for control group

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.6
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)
```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


## Scenario 9: rho = 0.3 for treatment and rho = 0.3 for control group

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.3
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


## Scenario 10: rho = 0.3 for treatment and rho = 0.2 for control group

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.2
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)
```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


# Perturbation of Residuals

## Scenario 11: sigma_r1=sigma_r2=sigma_r3=2 for treatment, sigma_r1=2, sigma_r2=2.5, sigma_r3=3 for control

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = c(2,2.5,3)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


## Scenario 12: sigma_r1=sigma_r2=sigma_r3=2 for treatment, sigma_r1=2, sigma_r2=1.5, sigma_r3=1 for control

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = c(2,1.5,1)
rho_c = 0.3
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


## Scenario 13: sigma_r1=sigma_r2=sigma_r3=2 for treatment, sigma_r1=2, sigma_r2=2, sigma_r3=2 for control. rho_r for control = 0.4.

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)


# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.4
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


## Scenario 14: sigma_r1=sigma_r2=sigma_r3=2 for treatment, sigma_r1=2, sigma_r2=2, sigma_r3=2 for control. rho_r for control = 0.2.

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.2
R_t=ar1_cor(p,sd_t,rho_t)
R_c=ar1_cor(p,sd_c,rho_c)

```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```


## Scenario 15: Exchangeable correlation, sigma_r1 = sigma_r2 = sigma_r3 = 2, rho_r = 0.3

```{r}
# Fixed effect `alpha` in equation 3.1.
alpha_t = c(55,4)
alpha_c = c(55,2)

# Covariance matrix `D` of random effect `b` in equation 3.1.
sigma_int_t = 5.5
sigma_int_c = 5.5
sigma_time1_t = 3.5
sigma_time1_c = 3.5
corr_t = 0.3
corr_c = 0.5
D_t = matrix(c(sigma_int_t^2, corr_t*sigma_int_t*sigma_time1_t, corr_t*sigma_int_t*sigma_time1_t, sigma_time1_t^2), nrow=2)
D_c = matrix(c(sigma_int_c^2, corr_c*sigma_int_c*sigma_time1_c, corr_c*sigma_int_c*sigma_time1_c, sigma_time1_c^2), nrow=2)

# Covariance matrix `R` of residuals `e` in equation 3.1.
p=3
sd_t <- rep(2,p)
rho_t <- 0.3
sd_c = rep(2,p)
rho_c = 0.3
R_t=exch_cor(p,sd_t,rho_t)
R_c=exch_cor(p,sd_c,rho_c)
```

```{r}
# Truth
cal_truth(n=5000,p=3,nsim=10000,alpha=list(alpha_t=alpha_t, alpha_c=alpha_c), D=list(D_t=D_t, D_c=D_c), R=list(R_t=R_t, R_c=R_c), convert_long)
```



